Simulation Figures for Genome Biology (simulations)

### 2018-06-11 manuscript_figures/manuscript_figures_sims.Rmd
Add zoomed/unzoomed noise plots

```{r, fig.width = 15, fig.height = 7.5}
plot_grid(pfdr + guides(color = FALSE, linetype = FALSE), ptpr)

gp <- plot_grid(pfdr + coord_cartesian(c(0, .2), c(0, .2)) + guides(color = FALSE, linetype = FALSE),
                ptpr + coord_cartesian(c(.6, 1), c(.6, 1)), rel_widths = c(1, 1.4), labels = LETTERS[1:2])
gp

ggsave(file.path(outdir, "FigureSsim-noise.pdf"), gp, width = 15, height = 7.5)
```

>>>>

```{r, fig.width = 15, fig.height = 7.5}
gp <- plot_grid(pfdr + guides(color = FALSE, linetype = FALSE), ptpr, , rel_widths = c(1, 1.4), labels = LETTERS[1:2])
gp

ggsave(file.path(outdir, "FigureSsim-noise.pdf"), gp, width = 11, height = 4.5)

gp_zoom <- plot_grid(pfdr + coord_cartesian(c(0, .2), c(0, .2)) + guides(color = FALSE, linetype = FALSE),
                     ptpr + coord_cartesian(c(.6, 1), c(.6, 1)), rel_widths = c(1, 1.4), labels = LETTERS[1:2])
gp_zoom

ggsave(file.path(outdir, "FigureSsim-noise-zoom.pdf"), gp_zoom, width = 11, height = 4.5)
```
